Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-31 doc/peakcharacterization_manuscript.Rmd
got unassigned peak matching and description of results done
related to #11

>>>>

::: {custom-style="MDPI_2.2_heading2"}
### Method Specific Peaks
:::

```{r increment_peak_comparisons}
table_count$increment("unassigned_1ecf")
table_count$increment("unassigned_97lipid")

figure_count$increment("unassigned_upset")

tar_load(um_peaks_1ecf)
tar_load(um_peaks_97lipid)
```

::: {custom-style="MDPI_3.1_text"}
Each set of peaks generated may or may not be specific to the particular method used to generate centroided peak m/z and intensities.
This is true for the different scan-centric combinations, as well as the peaks from Xcalibur and MSnbase.
Here we examine the overlap of the unassigned (`r figure_count$label_text("unassigned_upset")`) and assigned peaks from the full scan-centric processing with Xcalibur and MSnbase.
These same counts are also summarized in `r table_count$label_text("unassigned_1ecf")` and `r table_count$label_text("unassigned_97lipid")`.
In these two examples, there are some striking differences.
The 1ecf sample has all of the scan-centric peaks shared with either Xcalibur or MSnbase peaks, whereas the 97lipid sample has 2/3 of the peaks specific to scan-centric characterization and not matched to either of the other methods.
Notably, for both samples, the scan-centric characterization produces similar numbers of peaks, even though the upper mass limit in 1ecf is 1000 m/z compared to 1600 m/z for the 97lipid sample.
Whereas the number of peaks from MSnbase and Xcalibur are three-fold and 40-fold higher in the 1ecf sample compared to the 97lipid sample.
:::

```{r unassigned_upset, dn_id = figure_count, fig.width = 16, fig.height = 8}
set_order = c("scancentric", "msnbase", "xcalibur")
u1 = grid::grid.grabExpr(draw(UpSet(um_peaks_1ecf$comb_matrix, 
                           set_order = set_order)))
u2 = grid::grid.grabExpr(draw(UpSet(um_peaks_97lipid$comb_matrix, 
                           set_order = set_order)))

up_plot = wrap_elements(u1, clip = FALSE) + wrap_elements(u2, clip = FALSE)
up_plot + plot_annotation(tag_levels = "A")
```

::: {custom-style="MDPI_5.1_figure_caption"}
`r figure_count$label_text("unassigned_upset")`.
UpSet plot with the counts of common and specific peaks for each of scancentric, MSnbase and XCalibur generated peaks for the 1ecf (**A**) and 97lipid (**B**) samples.
:::

::: {custom-style="MDPI_4.1_table_caption"}
`r table_count$label_text("unassigned_1ecf")`.
Number of matched peaks between peak processing methods for 1ecf.
:::
::: {custom-style="MDPI_4.2_table_body"}
```{r unassigned_1ecf}
um_peaks_1ecf$ft_table %>%
  autofit()
```
:::

::: {custom-style="MDPI_4.1_table_caption"}
`r table_count$label_text("unassigned_97lipid")`.
Number of matched peaks between peak processing methods for 97lipid.
:::
::: {custom-style="MDPI_4.2_table_body"}
```{r unassigned_97lipid}
um_peaks_97lipid$ft_table %>%
  autofit()
```
:::
